Alternative Methods for Implementing Explicit and Finding Implicit Sharing in embedded DSLs

### 2022-12-12 paper/paper.tex
initial paper/prototype setup

\section{Examples TODO REMOVE ME}
example citiation \cite{kiselyov:sharing}
\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

>>>>

TODO describe sharing problem (mention observable sharing
\cite{gill:observablesharing} and implicit/explicit sharing
\cite{kiselyov:sharing} papers)

TODO describe finally tagless \cite{carette:finallytagless}

TODO overview of our method

\section{Detecting Sharing In Finally Tagless DSLs}
TODO

\section{Implicit Sharing Via Hash-Consing}
TODO
cite Ershov’s original description of hash-consing \cite{ershov1958:consing}
cite Type safe consing implementation (with performance benchamrks) \cite{filliatre:typesafeconsing}

\section{Limitations of Hash-Consing}

TODO add-chains example

\subsection{Explicit Sharing and Limitations}
TODO

\section{Implicit Sharing Via ByteString ASTs}
TODO

\subsection{Memory Limitations}
TODO
\section{Explicit Sharing Of ByteString ASTs}
TODO
